Operational constraints and closing civic space: International NGO restrictions and China’s Overseas NGO law

### 2023-12-04 manuscript/manuscript.qmd
Omitted a "TA"

```{r fig-ro-ta-pathways, fig.width=6, fig.height=3}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Two possible pathways for international NGOs to legally work in 
#|   China under the 2017 ONGO law, either as formal Registered Organizations 
#|   (ROs) or by undertaking specific Temporary Activities (TAs)"

>>>>

```{r fig-ro-ta-pathways, fig.width=6, fig.height=3}
#| echo: false
#| include: true
#| warning: false
#| message: false
#| fig-cap: "Two possible pathways for international NGOs to legally work in 
#|   China under the 2017 ONGO law, either as formal Representative Offices 
#|   or by undertaking specific Temporary Activities"
